>

### 2025-03-12 docs/article.qmd
Revise the abstract to below 250 words

format:
  elsevier-pdf:
    keep-tex: true
    include-in-header:
      file: _header.tex
    journal:
      formatting: review
      cite-style: authoryear
  docx:
    pandoc-options: ["--mathml"]

@@

metadata-files:
  - _author.yml
  - _abstract.yml
  - _knitr-bib.yml

@@

The inherently complex nature of health-related phenomena have fueled the growing implementation of network analysis, making it an important research framework in medicine and epidemiology [@Luke2007]. Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network. Only recently, @Cavallo2012 demonstrated a novel framework to describe medication uses on a population level, i.e. drug prescription network (DPN), a term which later is coined by @Bazzoni2015. Network analysis and graph theory offer an approach to model the relationship among building blocks of a complex system. From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021]. DPN can capture the complex relationships of a system that may vary overtime, which is highly relevant to drug prescribed for mental disorders.

In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013]. With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy. Same-class polypharmacy is the use of multiple medications from the same class. Multi-class polypharmacy is the use of multiple medications from different classes indicated for the same symptom cluster. Adjunctive polypharmacy is the use of additional medications to treat side effects due to other medications. Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster. Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike [@Shrivastava2013]. For policymakers, differences in defining polypharmacy pose a challenge to design a monitoring system [@Sirois2016].

@@

This study is an egocentric network analysis of two population groups: individuals receiving antidepressants and those receiving anxiolytics. By examining co-prescription patterns, we aimed to understand the prevalence and nature of polypharmacy within these groups. The rate of polypharmacy differs between these two groups. While same-class polypharmacy is more prevalent among individuals treated with antidepressants than among those treated with anxiolytics, multi-class polypharmacy predominates among those treated with anxiolytics. In both groups, multi-class polypharmacy is ten times more prevalent than same-class polypharmacy. The high prevalence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the prevalence of psychopharmaca polypharmacy [@de2004polypharmacy]. This highlights the interconnected nature of psychopharmaca prescription patterns.

>>>>

format:
  elsevier-pdf:
    keep-tex: true
    include-in-header:
      file: _header.tex
    journal:
      formatting: review
      cite-style: authoryear
    output-file: iadb-network-analysis.pdf
  docx:
    pandoc-options: ["--mathml"]
    output-file: iadb-network-analysis.docx

@@

metadata-files:
  - _author.yml
  - _abstract-short.yml
  - _knitr-bib.yml

@@

The inherently complex nature of health-related phenomena have fueled the growing implementation of network analysis, making it an important research framework in medicine and epidemiology [@Luke2007]. Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network. Only recently, @Cavallo2012 demonstrated a novel framework to describe medication use on a population level, i.e. drug prescription network (DPN), a term which later is coined by @Bazzoni2015. Network analysis and graph theory offer an approach to model the relationship among building blocks of a complex system. From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021]. DPN can capture the complex relationships of a system that may vary over time, which is highly relevant to drugs prescribed for mental disorders.

In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications. With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy [@Shrivastava2013]. Same-class polypharmacy is the use of multiple medications from the same class. Multi-class polypharmacy is the use of multiple medications from different classes indicated for the same symptom cluster. Adjunctive polypharmacy is the use of additional medications to treat side effects due to other medications. Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster. Finally, total polypharmacy is the total count of all medications used by a patient, both psychopharmaca and other classes alike [@Shrivastava2013]. For policymakers, differences in defining polypharmacy pose a challenge to design a monitoring system [@Sirois2016].

@@

This study is an egocentric network analysis of two population groups: individuals receiving antidepressants and those receiving anxiolytics. By examining co-prescription patterns, we aimed to understand the nature of polypharmacy within these groups. The rate of polypharmacy differs between these two groups. While same-class polypharmacy is more prevalent among individuals treated with antidepressants than among those treated with anxiolytics, multi-class polypharmacy predominates among those treated with anxiolytics. In both groups, multi-class polypharmacy is ten times more prevalent than same-class polypharmacy. The high occurrence of multi-class polypharmacy in our findings aligns with previous studies, which show that antidepressants and anxiolytics are often co-prescribed with other medications [@Shrivastava2013], and multi-class regimens contribute the most to the occurrence of psychopharmaca polypharmacy [@de2004polypharmacy]. This highlights the interconnected nature of psychopharmaca prescription patterns.
